\documentclass{report}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}


% Packages
% Add any additional packages you need here

% Document information
\title{Your Thesis Title}
\author{Your Name}
\date{\today}

\geometry{
    a4paper,
    left=30mm,
    right=30mm,
    top=30mm,
    bottom=30mm
}

\begin{document}

% Title page
\maketitle

% Abstract
\begin{abstract}
% Add your abstract here
\end{abstract}

% Table of contents
\tableofcontents

% Chapters
\chapter{Introduction}
% Add your introduction chapter here

\chapter{Literature Review}
\include{chapters/literaturereview}

\chapter{Methodology}
\include{chapters/methodology}
% Add more chapters as needed

\chapter{Implementation}
\include{chapters/implementation}

\chapter{Project Management}

\chapter{Evaluation}
\include{chapters/evaluation}

\chapter{Discussion}

% Conclusion
\chapter{Conclusion}
% Add your conclusion chapter here
\chapter{Appendix}
\include{chapters/appendix}
% References
\begin{thebibliography}{}
    \bibitem{1} R. Paul, R. R. Bhandopia, D. R. Patil, J. D. Raut, and A. D. Gotmare, ‘An Efficient Digital Ordering System for Restaurant’, Ijresm.com. [Online]. Available: \url{https://www.ijresm.com/Vol.3_2020/Vol3_Iss3_March20/IJRESM_V3_I3_103.pdf}. [Accessed: 17-Mar-2024].

    \bibitem{2} ‘(PDF) Smart QR-based Restaurant Dine-in System with Sales Analysis’, ResearchGate. [Online]. Available: \url {https://www.researchgate.net/publication/360414606_Smart_QR-based_Restaurant_Dine-in_System_with_Sales_Analysis/fulltext/627a7d2b2f9ccf58eb3d5475/Smart-QR-based-Restaurant-Dine-in-System-with-Sales-Analysis.pdf}. [Accessed: 17-Mar-2024].

    \bibitem{3}D. Carcache and R. E, “Automated Services Order System,” prcrepository.org, 2013, Accessed: Mar. 17, 2024. [Online]. Available: \url {https://prcrepository.org/xmlui/handle/20.500.12475/836?show=full}

    \bibitem{4} K. Dhiman, “Online Food Ordering Management System,” International Journal for Research in Applied Science and Engineering Technology, vol. 9, no. VII, pp. 2096–2107, Jul. 2021, doi: {https://doi.org/10.22214/ijraset.2021.36835}.
    
    \bibitem{5} ‘(PDF) Customer Acceptance of QR Menu Ordering System in Luxury Restaurants. A study of Xi’an, China’, ResearchGate. [Online]. Available: \url{https://www.researchgate.net/profile/Anshul-Garg-4/publication 377586294_Customer_Acceptance_of_QR_Menu_Ordering_System_in_Luxury_Restaurants_A_study_of_Xi'an_China/links/65ae68e29ce29c458b939be6/Customer-Acceptance-of-QR-Menu-Ordering-System-in-Luxury-Restaurants-A-study-of-Xian-China.pdf}. [Accessed: 17-Mar-2024].

    \bibitem{6}
    B. Shadaksharappa, Kotrachaithanya, and D. Kumar, “FOOD HUB A Model for Ordering In Restaurant Based On Qr Code Without Presence Of A Waiter At The Table,” International Journal of Engineering Research in Computer Science and Engineering (IJERCSE), vol. 5, no. 5, pp. 2394–2320, 2018, Available: \url{https://www.technoarete.org/common_abstract/pdf/IJERCSE/v5/i5/Ext_34756.pdf}.

    \bibitem{7}
    E. E. Abel and E. Obeten, ‘Restaurant customer self-ordering system: A solution to reduce customer/guest waiting time at the Point of sale’, Ijcaonline.org. [Online]. Available: \url{https://research.ijcaonline.org/volume111/number11/pxc3901332.pdf}. [Accessed: 17-Mar-2024].


    \bibitem{8} Toast, Inc., "Toast: Restaurant Point of Sale and Management System," [Online]. Available: \url{https://pos.toasttab.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{9} Square, Inc., "Square: Solutions For Your Small, Medium and Large Business," [Online]. Available: \url{https://squareup.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{10} Zuppler, "Zuppler: Online Ordering System for Restaurants," [Online]. Available: \url{https://www.zuppler.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{11} TouchBistro Inc., "TouchBistro: iPad POS System for Restaurants, Bars, and More," [Online]. Available: \url{https://www.touchbistro.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{12} Bbot, "Bbot: Contactless Order and Pay," [Online]. Available: \url{https://www.bbot.menu/}. [Accessed: Mar. 17, 2024].

    \bibitem{13} Menufy, "Menufy: Online Ordering for Restaurants," [Online]. Available: \url{https://www.menufy.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{14} Future Ordering, "Future Ordering: Digital Ordering Solutions," [Online]. Available: \url{https://www.futureordering.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{15} React Team, "React – A JavaScript library for building user interfaces," React. [Online]. Available: \url{https://reactjs.org/}. [Accessed: Mar. 17, 2024].

    \bibitem{16} Django Software Foundation, "Django: The web framework for perfectionists with deadlines," Django. [Online]. Available: \url{https://www.djangoproject.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{17} SQLite, "SQLite Home Page," SQLite. [Online]. Available: \url{https://sqlite.org/index.html}. [Accessed: Mar. 17, 2024].

    \bibitem{18} Axios, "Axios GitHub repository," GitHub. [Online]. Available: \url{https://github.com/axios/axios}. [Accessed: Mar. 17, 2024].

    \bibitem{19} D. Abramov and A. Clark, "Introducing Hooks," React, Oct. 25, 2018. [Online]. Available: \url{https://reactjs.org/docs/hooks-intro.html}. [Accessed: Mar. 17, 2024].

    \bibitem{20} T. Otwell, "Laravel: The PHP Framework For Web Artisans," Laravel. [Online]. Available: \url{https://laravel.com}. [Note: Replace with Django REST Framework if specific documentation is available]. [Accessed: Mar. 17, 2024].

    \bibitem{21} React Router, "React Router: Declarative Routing for React.js," ReactRouter. [Online]. Available: \url{https://reactrouter.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{22} Bulma, "Bulma: a modern CSS framework based on Flexbox," Bulma. [Online]. Available: \url{https://bulma.io/}. [Accessed: Mar. 17, 2024].

    \bibitem{23} AWS, "Amazon Web Services (AWS) - Cloud Computing Services," Amazon. [Online]. Available: \url{https://aws.amazon.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{24} Heroku, "Heroku: Cloud Application Platform," Heroku. [Online]. Available: \url{https://www.heroku.com/}. [Accessed: Mar. 17, 2024].

    \bibitem{25} Railway, "Railway: Infrastructure for modern applications," Railway. [Online]. Available: \url{https://railway.app/}. [Accessed: Mar. 17, 2024].

    \bibitem{26}Real Python, “Build a Recommendation Engine With Collaborative Filtering,” Realpython.com, Jul. 10, 2019. https://realpython.com/build-recommendation-engine-collaborative-filtering/ (accessed Mar. 22, 2024)

    \bibitem{27}“What Is Collaborative Filtering: A Simple Introduction,” Built In, 2019. https://builtin.com/data-science/collaborative-filtering-recommender-system (accessed Mar. 22, 2024).

    \bibitem{28} Shivam Baldha, “Introduction to Collaborative Filtering,” Analytics Vidhya, Feb. 25, 2022. https://www.analyticsvidhya.com/blog/2022/02/introduction-to-collaborative-filtering/ (accessed Mar. 22, 2024).

    \bibitem{29} A. Roy, “Introduction To Recommender Systems- 1: Content-Based Filtering And Collaborative Filtering,” Medium, Jul. 29, 2020. https://towardsdatascience.com/introduction-to-recommender-systems-1-971bd274f421 (accessed Mar. 22, 2024).

    \bibitem{30} Hybrid Recommender Systems, “Hybrid Recommender Systems | Saturn Cloud,” Saturncloud.io, Feb. 23, 2023. https://saturncloud.io/glossary/hybrid-recommendation-system/ (accessed Mar. 22, 2024).

    \bibitem{31} Sciforce, “Deep Learning Based Recommender Systems - Sciforce - Medium,” Medium, Apr. 30, 2021. https://medium.com/sciforce/deep-learning-based-recommender-systems-b61a5ddd5456 (accessed Mar. 22, 2024).

    \bibitem{32} Krishnakanth Naik Jarapala, “Understanding Gale-Shapley (Stable Matching ) Algorithm and its Time Complexity,” Medium, Jan. 31, 2023. https://medium.com/aiskunks/understanding-gale-shapley-stable-matching-algorithm-and-its-time-complexity-4b814ee2642 (accessed Mar. 22, 2024).

    \bibitem{33} “How Netflix’s Recommendations System Works,” Help Center, 2024. https://help.netflix.com/en/node/100639 (accessed Mar. 23, 2024).

    \bibitem{34} M. Geuens, “Research on Influencing Factors of Food Choice and Food Consumption,” Foods, vol. 12, no. 6, pp. 1306–1306, Mar. 2023, doi: https://doi.org/10.3390/foods12061306.

    \bibitem{35} Ingrid H.M. Steenhuis, W. E. Waterlander, and Anika de Mul, “Consumer food choices: the role of price and pricing strategies,” Public Health Nutrition, vol. 14, no. 12, pp. 2220–2226, Jul. 2011, doi: https://doi.org/10.1017/s1368980011001637.
    ‌
    ‌
    ‌
    ‌
    ‌
    ‌
    ‌
    ‌
    ‌
    ‌







    

\end{thebibliography}

\end{document}